

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Getting Started}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


This chapter provides instructions for building, installing, and running \SIM.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Documentation and Other Support}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\SIM is hosted on github at the following URL:
\urlc{https://github.com/macsimgt/macsim-public }. 
The project page for \SIM on
Google Code provides stable version of \SIM, detailed documentation,
issue/bug tracking, sample traces and so on. Users can use the project
page for filing issues and for contacting the maintainers of \SIM.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Building \SIM}
\label{sec:installation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Obtaining Source}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\SIM source code is maintained using subversion. Users can obtain a copy of the
source code using this command:

\begin{Verbatim}
svn co https://svn.research.cc.gatech.edu/macsim/trunk macsim-readonly --username readonly
\end{Verbatim}

\noindent
Note that currently password is not set for the readonly account. Press `enter' when you are prompted for a password. Due to a technical issue, we do
not allow anonymous checkout right now. The documentation will be updated when this issue is resolved.

Users will have read-only permission by default and users interested
in contributing to \SIM must contact
\href{mailto:macsim-dev@googlegroups.com}{macsim-dev@googlegroups.com}.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Requirements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To build \SIM the following are required:

\begingroup
\renewcommand\descriptionlabel[1]{\textit{\hspace\labelsep{#1}}}
%\renewcommand\descriptionlabel[1]{\hspace\labelsep\cs{#1}}
\begin{description}\firmlist
  \item[Operating System]- At present only Linux distributions are supported. \SIM has been tested on:
   \Verb!Ubuntu 12.04 +!, \Verb!RHEL 6+!, \Verb+MacOS(10.10.5)+
  \item[Compiler]- Any compiler that supports the C++0x (or C++11)
    standard. \SIM has been verified to work with: \Verb+gcc 4.4 or higher+, \Verb+icc (should work)+
  \item[SConstruct]- For Ubuntu, \Verb+apt-get install scons+. For RHEL, enable EPEL followed by \Verb+yum install scons+. 

\ignore
	 {
	  \item[Autotools] - Autotools (automake, autoconf,
		...) version 2.65 or higher is required. Autotools can be installed using the commands:
	\begin{Verbatim}
	Ubuntu: apt-get install autotools-dev automake autoconf
	\end{Verbatim}
	}
  
  \item[Libraries]- zlib and other dependencies can be installed using the following commands:
\begin{Verbatim}
Ubuntu: apt-get install zlib1g-dev
RHEL: yum groupinstall "Development Tools" && yum install zlib-devel zlib-static libstdc++-static glibc-static 
\end{Verbatim}
\end{description}
\endgroup




\ignore{
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \subsection{Directory Structure}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	  This section explains the directory structure of \SIM simulator.

	  \smallskip
	  \begin{lstlisting}
	  macsim/
		tag/ branch/ trunk/
	  \end{lstlisting}
	  \smallskip

	  \textit{Tag} directory has tagged version of \SIM
	  simulators. \textit{Branch} directory is for diverged \SIM, which is
	  currently empty. \textit{Trunk} directory is current working directory
	  for \SIM.

	  Following is more detailed information about \textit{Trunk} directory.

	  \smallskip
	  \begin{lstlisting}
	  trunk/
		bin/ def/ doc/ params/ scripts/ src/ tools/
	  \end{lstlisting}
	  \smallskip

	  \textit{Bin} directory contains the \SIM binary after the building
	  process. \textit{def} directory has knob (Section~\ref{sec:knob}) and
	  statistics (Section~\ref{sec:stat}) definitions. \textit{doc} has the
	  documentation. \textit{scripts} includes several scripts files that
	  are using during the building process. \textit{src} contains all
	  source files. \textit{tools} has several useful tools.
	  \ignore{ (Section~\ref{sec:tool}) }
	  }

\ignore
	  {
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \subsection{Source organization}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	  \TODO{check this, i'm not sure what is included in the copy that be available
		publically} 

	  The top-level source directory of \SIM contains several source, script and tool
	  directories, README and INSTALL files and files required for building \SIM
	  using autotools. Below is a brief description of the contents of the top-level
	  source directory of \SIM.


	  \begin{description}\firmlist

	  \item [bin] Build output directory.

	  \item [def] Contains definitions of parameters (see Sections~\ref{sec:run}
		  and~\ref{sec:knob}) and events for statistics (see Section~\ref{sec:stat}).

	  \item [doc] Contains \SIM documentation.

	  \item [params] Contains sample parameter (see Sections~\ref{sec:run}
		  and~\ref{sec:knob}) configuration files.

	  \item [scripts] Contains scripts used in build of \SIM.

	  \item [src] Contains \SIM source files (.cc and .h files).

	  \item [tools] Contains x86 trace generator and trace reader.

	  \item [README, INSTALL] README and INSTALL files containing proceduce to build
	  and run \SIM and patch \SIM to make it usable as a SST component (see
		  Section~\ref{sec:sst}).

	  \item [autogen.sh] Script file to generate makefile to build \SIM.

	  \item [configure.in aclocal.m4 Makefile.am Makefile.in] Files required by
	  autotools to generate makefile to build \SIM.


	  \end{description}
	  }

\ignore
	  {
		The top-level source directory of \SIM contains several directories including
		\Verb+bin+, \Verb+def+, \Verb+doc+, \Verb+params+, \Verb+scripts+, \Verb+src+ and
		\Verb+tools+ and the \Verb+README+ and \Verb+INSTALL+ files and the files
		required for building \SIM using autotools.
	  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Build}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

SConstruct is used to build \SIM. After checking out a copy of the
\SIM source code, the following commands have to be executed (These
instructions are also available in \Verb+INSTALL+ file included in the
\SIM source). Section~\ref{sec:buildoption} details all available build options.


\begin{Verbatim}
./build.py
\end{Verbatim}

\noindent
On a successful build, the binary \bin will be generated in the
\Verb+bin/+ directory. Please note that SST-Macsim still uses
GNU Autotools, so we maintain some related files (\Verb+Makefile.am+).


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Build Types}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Three types of build, each of which uses different compiler flags are
supported. The build types are:

\begin{itemize}
  \item Optimized version (-O3 flag) - default
  \item Debug version (-g3 flag)
  \item Gprof version (-pg flag)
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Build Options}
\label{sec:buildoption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are several options in \Verb+build.py+.

\begin{itemize}
  \item -j : specify the number of threads to be used for building \SIM.
  \item -d : debug version
  \item -p : gprof version
  \item -c : cleanup
  \item -t : build test
  \item - -dramsim : macsim with DRAMSim2 simulator (DRAM memory)
    (this option is deprecated)
  \item - -iris : macsim with Iris simulator (interconnection)  (this option is deprecated)
 
  \item - -power : macsim with power module (currently, not supported) 
\end{itemize}

\noindent
We also provide \Verb+macsim.config+ file to set the configuration instead of 
specifying options with the commandline. The following is the content of the 
\Verb+macsim.config+ file.

  \begin{Verbatim}
  [Build]
  debug: 0
  gprof: 0

  [Library]
  dram: 0
  power: 0
  iris: 0
  \end{Verbatim}

\noindent
Users can change the value to 1 for the corresponding option.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running \SIM}
\label{sec:run}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To run the \bin binary, two additional files are required to be present 
the same directory as the binary.

\begin{itemize}
  \item[1] \textbf{params.in} - defines architectural parameter values that will
  overwrite the default parameter values.

  \item[2] \textbf{trace\_file\_list} - specifies the number of traces to run and
  the location of each trace.
\end{itemize}


Several pre-defined architectural parameter configuration files are provided in
\Verb+params/+ directory. Table~\ref{table:param} lists the included
pre-defined parameter files. To run \SIM with a particular architectural
configuration, users should copy the corresponding parameter file to \Verb+bin/+
directory and rename it as \Verb+params.in+. For example, to use NVIDIA's
Fermi~\cite{fermi} GPU architecture, \Verb+params/params_gtx465+ should be
copied to \Verb+bin+ and renamed as \Verb+params.in+. 

\begin{table}[!h]
\begin{footnotesize}
\begin{center}
\caption{Parameter Templates.}
\label{table:param}
\begin{tabular}{|l|l|l|}
\hline
File Name              & Description & Architecture                         \\ \hline \hline
params\_8800gt         &             & NVIDIA GeForce 8800 GT (G80)         \\
params\_gtx280         &             & NVIDIA GeForce GTX 280 (GT200)       \\
params\_gtx465         &             & NVIDIA GeForce GTX 465 (Fermi)       \\
params\_x86            &             & Intel's Sandy Bridge (CPU part only) \\
params\_hetero\_4c\_4g &             & Intel's Sandy Bridge (CPU + GPU)     \\ \hline
\end{tabular}
\end{center}
\end{footnotesize}
\end{table}


\noindent \Verb+trace_file_list+ specifies the list of traces to be simulated. Following is the
content of a sample \Verb+trace_file_list+: \\

\begin{tabular}[!h]{l l}
 \Verb+2+	& \Verb+<-- number of traces+ \\
 \Verb+/trace/ptx/cuda2.2/FastWalshTransform/kernel_config.txt+	& \Verb+<-- trace #1 path+ \\
 \Verb+/trace/ptx/cuda2.2/BlackScholes/kernel_config.txt+	& \Verb+<-- trace #2 path+ \\
 & \\
\end{tabular}


\noindent 	Above, the first line specifies the number of traces (applications) that will
be simulated and each line thereafter specifies the path to the trace
configuration file in the trace directory of an application. The contents of a
sample trace configuration file are shown below.

\begin{Verbatim}
1 x86
0 0
\end{Verbatim}

\noindent In the first line, the first field indicates the number of threads in
the application (1 in this case) and the second field specifies the type of the
application (x86 in this case). Other lines contain a thread id and the starting 
point of the thread in terms of the instruction count of the main thread
(thread 0).


Several sample trace files are available at
\urlc{http://code.google.com/p/macsim}. Users can generate their own
traces by following instructions in Chapter~\ref{ch:trace}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Executing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \SIM simulator can be run by executing the \bin binary located in the
\Verb+bin/+ directory.

\begin{Verbatim}
./macsim
\end{Verbatim}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Output Files}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\SIM generates a \Verb+params.out+ file and several files \Verb+*.stat.out+
containing statistics at the end of a successful simulation. Users can specify
the output directory for these files by setting the
\Verb+STATISTICS\_OUT\_DIRECTORY+ parameter whose default value is the
directory containing the \bin binary.

	  \ignore{
	  several output files once the simulation is completed successfully.
	  Here are the list of output files.

	  \begin{Verbatim}
	  params.out
	  statfile1.stat.out
	  statfile2.stat.out
	  ...
	  statfilen.stat.out
	  \end{Verbatim}
	  }

\noindent \Verb+params.out+ enumerates all parameters with their values used
for the simulation. Simulation parameters are discussed in detail in 
section~\ref{sec:knob}. The \Verb+*.stat.out+ files contain statistics such as the number
of simulation cycles and so on. Chapter~\ref{sec:stat} details the kinds of
statistics supported, how to add new statistics and how to examine and
interpret the contents of \Verb+.stat.out+ files.


\ignore
	  {
	  Other files are statistics outputs, which is mostly the number
	  of occurrence for architectural events during the simulation. Each
	  stat out file consists of following lines:

	  \begin{Verbatim}
	  STAT     Raw_counter_value     Value_per_type
	  \end{Verbatim}

	  \noindent
	  , where \Verb+STAT+ is the name of stat, \Verb+Raw_counter_value+ is
	  the raw value of the counter, and \Verb+Value_per_type+ is the value
	  based on the each stat type. There are three types of statistics:

	  \begin{itemize}

		\item COUNT - for counting the number of occurances of an event. Eg. number
		of cache hits. 

		\item RATIO - for calculating the ratio of number of occurances of one event
		over another. Eg. (number of cache hits / number of cache accesses) i.e.,
		cache hit ratio.

		\item DIST - for defining a group of related events and calculating the
		number of occurances of each event in the as a percent of the sum of the
		number of occurances of all events in the group.  Eg. If we want to know what
		percent of L1 data cache accesses (in a 2-level hierarchy) resulted in L1
		hits, L2 hits or memory accesses, we should define a distribution consisting
		on three events - L1 hits, L2 hits and L2 misses  - and update the
		counter for each event correctly. 
	  \end{itemize}


	  \noindent
	  We sometimes need to measure a certain event per core, so we further
	  categorize statistics into either global (common counter for all
	  cores) or per core (each core has its own counter). The suffix of all
	  per core stats is \Verb+_CORE_#+. Chapter~\ref{sec:stat} details
	  regarding statistics.


	  \begin{table}[htb]
	  \begin{footnotesize}
	  \begin{center}
	  \caption{Important Stats.} 
	  \label{table:stats}
	  \begin{tabular}{|l||l|c|l|}
	  \hline 
	  STAT & Description & Per-Core & Filename \\ \hline \hline
	  INST\_COUNT\_TOT            & \# of instructions                                    &      & general.stat.out \\ \hline 
	  INST\_COUNT\_CORE\_[0-11]   & \# of instructions in only the specificed core [0-11] & core & general.stat.out \\ \hline 
	  CYC\_COUNT\_TOT             & simulated cycles                                      &      & general.stat.out \\ \hline 
	  CYC\_COUNT\_CORE\_[0-11]    & simulated cycles in only the specificed core [0-11]   &      & general.stat.out \\ \hline 
	  CYC\_COUNT\_X86             & simulated cycles for x86 only                         &      & general.stat.out \\ \hline 
	  CYC\_COUNT\_PTX             & simulated cycles for ptx only                         &      & general.stat.out \\ \hline \hline 
								  & \# of fp instructions                                 &      &                  \\ \hline 
								  & \# of int instructions                                &      &                  \\ \hline 
								  & \# of load instructions                               &      &                  \\ \hline  
								  & \# of store instructions                              &      &                  \\ \hline  
	  BP\_ON\_PATH\_CORRECT       & \# of correctly predicted branches (DIST)             & core & bp.stat.def      \\ \hline  
	  BP\_ON\_PATH\_MISPREDICT    & \# of mis-predicted branches (DIST)                   & core & bp.stat.def      \\ \hline  
	  BP\_ON\_PATH\_MISFETCHT     & \# of mis-fetch branches (BTB MISS)(DIST)             & core & bp.stat.def      \\ \hline  
	  ICACHE\_HIT, ICACHE\_MISS   & \# of I-cache hitt,miss (DIST)                        &      & memory.stat.def  \\ \hline  
	  L[1-3]\_HIT\_CPU            & \# of l[1-3]cache hits from CPU                       &      & memory.stat.def  \\ \hline 
	  L[1-3]\_HIT\_GPU            & \# of l[1-3]cache hits from GPU                       &      & memory.stat.def  \\ \hline 
	  L[1-3]\_MISS\_CPU           & \# of l[1-3]cache misses from CPU                     &      & memory.stat.def  \\ \hline 
	  L[1-3]\_MISS\_GPU           & \# of l[1-3]cache misses from GPU                     &      & memory.stat.def  \\ \hline  \hline 
	  AVG\_MEMORY\_LATENCY        & average memory latency                                &      & memory.stat.def  \\ \hline \hline 
	  TOTAL\_DRAM                 & \# of DRAM accesses                                   &      & memory.stat.def  \\ \hline  
	  TOTAL\_DRAM\_READ           & \# of DRAM reads                                      &      & memory.stat.def  \\ \hline  
	  TOTAL\_DRAM\_WB             & \# of DRAM write backs                                &      & memory.stat.def  \\ \hline  
								  & \# of register reads                                  &      &                  \\ \hline  
								  & \# of register writes                                 &      &                  \\ \hline   \hline 
	  COAL\_INST, UNCOAL\_INST    & coalesced/uncoalesced mem requests (DIST)             &      & memory.stat.def  \\ \hline 
	  \end{tabular}
	  \end{center}
	  \end{footnotesize}
	  \end{table} 


	  You can 


	  \begin{Verbatim}
	  IPC = INST_COUNT_TOT / CYC_COUNT_TOT
	  CPI = CYC_COUNT_TOT / INST_COUNT_TOT
	  \end{Verbatim}

	  \begin{Verbatim}
	  IPC_1 = INST_COUNT_CORE_1 / CYC_COUNT_CORE_1
	  IPC_2 = INST_COUNT_CORE_2 / CYC_COUNT_CORE_2
	  ...
	  IPC = harmonic_mean(IPC_1, IPC_2, ..., IPC_n)

	  \end{Verbatim}


	  Table~\ref{table:stats} shows important stats.
	  }



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SST-MacSim}
\label{sec:sst}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Structural Simulation Toolkit (SST)~\cite{sst} is an MPI-based 
simulation framework, on which multiple simulators can communicate 
and run over multiple nodes. 
\SIM provides SST component wrappers and this section provides 
instructions to use \SIM as an SST component.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Building SST}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The instructions for building SST can be found at 
\urlc{https://www.sst-simulator.org/}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Building \SIM as a SST component}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Checkout \SIM from our SVN or GitHub repository (\urlc{https://github.com/macsimgt/macsim-public}) under \textit{<sst-root>/sst/elements}.
Make sure to change the name of the directory as \textit{macsimComponent}.

\begin{Verbatim}
cd <sst-root>/sst/elements
svn co https://svn.research.cc.gatech.edu/macsim/trunk macsimComponent
--username readonly 
\end{Verbatim}
Re-build the SST in order for \SIM to be included in the build procedure.

\begin{Verbatim}
cd <sst-root>
./autogen.sh
./configure --prefix=$SST_HOME --with-boost=$BOOST_HOME
make && make install
\end{Verbatim}
Some tips regarding building procedure are as follows.
\begin{itemize}
  \item To print debug messages, add \textit{--enable-debug} to the configure command.
  \item To adjust the optimization level, use \textit{CFLAGS or CXXFLAGS} when configuring. E.g., \textit{CFLAGS=-O0 CXXFLAGS=-O0}
  \item To exclude a component from SST build procedure, put \textit{.ignore} file in the component directory.
  \item After the initial build, you can just \textit{make \&\& make install} in the component directory without re-building entire SST.
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Example configuration}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

An example configuration is as follows.
Please note that parameters for other components but \SIM are omitted.
Sample configurations can be found in
<macsim-root>/sst-unit-test/.
Example files are sdl[1|2].py sdl[1|2].xml . runTest.py test the test
traces. 

\begin{Verbatim}
<?xml version="1.0"?>
<sdl version="2.0"/>
<timebase>1ns</timebase>

<variables>
  <lat> 1ps </lat>
  <buslat> 10 ps </buslat>
</variables>

<param_include>
  <macsimParams>
    <paramFile> params.in </paramFile>
    <traceFile> trace_file_list </traceFile>
    <outputDir> results </outputDir>
     <commandLine> --use_memhierarchy=1 </commandLine>
    <clockFreq> 1 Ghz </clockFreq>
    <printLocation> 0 </printLocation>
    <debugLevel> 8 </debugLevel>
  </macsimParams>
</param_include>

<sst>
  <component name="c0" type="macsimComponent.macsimComponent">
    <params include=macsimParams />
    <link name=c0_icache port=icache_link latency=$lat/>
    <link name=c0_dcache port=dcache_link latency=$lat/>
  </component>

  <component name="c0l1Icache" type="memHierarchy.Cache">
    <params include=l1IParams />
    <link name=c0_icache port=high_network_0 latency=$lat/>
    <link name=c0_icache_l2 port=low_network_0 latency=$buslat/>
  </component>

  <component name="c0l1Dcache" type="memHierarchy.Cache">
    <params include=l1DParams />
    <link name=c0_dcache port=high_network_0 latency=$lat/>
    <link name=c0_dcache_l2 port=low_network_0 latency=$buslat/>
  </component>

  <component name="c0l2cache" type="memHierarchy.Cache">
    <params include=l2Params />
    <link name=c0_icache_l2 port=high_network_0 latency=$lat/>
    <link name=c0_icache_l2 port=high_network_1 latency=$lat/>
    <link name=l2_mem port=low_network_0 latency=$buslat/>
  </component>

  <component name="memory0" type="memHierarchy.MemController">
    <params include=memParams />
    <link name=l2_mem port=direct_link latency=$buslat/>
  </component>
</sst>
\end{Verbatim}
Multiple instances of \SIM can be instantiated.
Each instance can be configured differently using its own params.in file, and can also run separate traces using its own trace\_file\_list file.
For instance, one \SIM instance can be configured as an X86 processor which runs one of the SPEC2006 benchmarks, while the other \SIM instance can be configured as a GPU which runs one of the CUDA benchmarks. 

\subsection{Running a \SIM simulation on top of SST framework}

Ensure that SST and \SIM components are successfully built and installed.  
Start the SST simulation either standalone or through MPI using the following commands.

\begin{Verbatim}
sst [sdl-file]
\end{Verbatim}
or
\begin{Verbatim}
mpirun -np [x] sst [sdl-file]
\end{Verbatim}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Using  SST's Memory Module}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

When \SIM is executed as an SST component, it can use other SST
components. MemHierarchy  is one of them.  MemHierarchy supports MESI
cache coherence and it also connects with other network modules such
as merlin. VaultSim models the HMC memory model.  Please refer to the SST homepage for other supported modules. 
In order to use MemHierarchy,  the command line sets {\texttt use\_memhierarchy} to 1 as shown in {\texttt sdl1.py} example in the sst-unit-test
directory.  

The code that is guarded with  {\texttt \#ifdef USING\_SST}  includes call
back functions to communicate with macsim.  Caches and DRAMS/3D memory
modules are modeled inside SST. 

\ignore
	  {
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \section{How to Get Memory Traces Using \SIM}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	  \todo{TODO}
	  }









