
\chapter{Internal Users Only Manual}
\section{Regression Tests}
\label{sec:regression}

To confirm your change does not affect the behavior of other parts,
regression test can be an useful tool. Let's say your current working
directory name is macsim-working. Here are steps to perform regression
test.

\begin{enumerate}[Step 1.]

\item You need to get a clean copy of macsim again. Let's say you are
  getting a new copy in macsim-regression directory.

\begin{Verbatim}
svn co https://svn.research.cc.gatech.edu/macsim/trunk macsim-regression --username user
\end{Verbatim}

\item You have to get a simulator tool, which is in the hparch svn
  repository.

\begin{Verbatim}
svn co https://svn.research.cc.gatech.edu/hparch/sim/trunk/tools tools --username user
\end{Verbatim}

\item Go to macsim-regression/trunk/bin directory and execute
  \Verb+regression_gen.py+ which is in your tool directory.

\begin{Verbatim}
cd macsim-regression/bin
regression_gen.py
\end{Verbatim}

\item Go to macsim-working/bin directory and execute
  \Verb+regression_test.py+ which is in your tool directory.

\begin{Verbatim}
cd macsim-working/bin
regression_test.py
\end{Verbatim}

\item Here is the output.

\begin{Verbatim}
regression_test.py
running ptx_fermi_6core BicubicTexture - 1 of 123
running ptx_fermi_6core BlackScholes1 - 2 of 123
running ptx_fermi_6core ConvolutionSeparable - 3 of 123
running ptx_fermi_6core ConvolutionTexture - 4 of 123
running ptx_fermi_6core Dct8x8 - 5 of 123
running ptx_fermi_6core Dxtc1 - 6 of 123
running ptx_fermi_6core FastWalshTransform - 7 of 123
running ptx_fermi_6core Histogram2561 - 8 of 123
...
Summary: total 123 pass 123 diff 0 fail 0
\end{Verbatim}

\end{enumerate}


\section{What to use internal directory}

TBD

