


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\SIM is a heterogeneous architecture simulator, which is trace-driven
and cycle-level. It thoroughly models architectural behaviors,
including detailed pipeline stages, multi-threading, and memory
systems. Currently, \SIM support x86 and NVIDIA PTX instruction set
architectures (ISA). \SIM is capable of simulating a variety of
architecreus, such as Intel's Sandy Bridge~\cite{sandybridge} and
NVIDIA's Fermi~\cite{fermi}.  It can simulate homogeneous ISA
multicore simulations as well as heterogeneous ISA multicore
simulations.

MacSim is a microarchitecture simulator that simulates detailed
pipeline stages (in-order and out-of-order) and the memory system components 
including caches, NoC, and memory controllers. It supports asymmetric 
multicore configurations as well as SMT or MT architectures.

%Currently interconnection network model (based on IRIS) and power
%model (based on McPat~\cite{mcpat}) are implemented. 

ARM ISA support is on-progress. To get the ARM traces for macsim,
please contact hyesoon@cc.gatech.edu. 

MacSim is also one of the components of SST~\cite{sst} so
multiple MacSim simulators can run concurrently.





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Macsim version information}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begingroup
\renewcommand\descriptionlabel[1]{\textit{\hspace\labelsep{#1}}}
%\renewcommand\descriptionlabel[1]{\hspace\labelsep\cs{#1}}
\begin{description}\firmlist
\item[2.2.0-  September 2015] 
  \Verb+macsim/tags/macsim-2.2.0/+
\item[2.1.1 - May 2015] 
  \Verb+macsim/tags/macsim-2.1.1/+
\item[2.1.0 - May 2015] 
  \Verb+macsim/tags/macsim-2.1.0/+
\item[2.0.4 - October, 2014] 
  \Verb+macsim/tags/macsim-2.0.4/+
\item[2.0.3 - August, 2014] 
  \Verb+macsim/tags/macsim-2.0.3/+
\item[2.0.2 - April, 2014] 
  \Verb+macsim/tags/macsim-2.0.2/+
\item[2.0 - September, 2013] 
  \Verb+macsim/tags/macsim-2.0/+
\item[1.2.1 - April, 2013] 
  \Verb+macsim/tags/macsim-1.2.1/+
\item[1.2 - October, 2012] 
  \Verb+macsim/tags/macsim_1.2+ 
\item[1.1 - October, 2012] 
  \Verb+macsim/tags/macsim_1.1+ 
\item[1.0 - February, 2012] Initial release
  \Verb+macsim/tags/macsim_1.0+ 
\end{description}
\endgroup


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Macsim Code Contributors}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The MacSim code is mainly developed at the HpArch research group. The
main source code contributors are as follows: Hyesoon Kim, Jaekyu Lee,  Nagesh B. Lakshminarayana, Jaewoong Sim,
Jieun Lim, Tri Pho, Hyojong Kim, Ramyad Hadidi.  This list keeps 
increasing as we add more features. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Macsim  Mailing List}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Please join macsim-dev@googlegroups.com for macsim mailing list. 
Internal developers use macsim-dev-hparch@googlegroups.com. If you
have  questions about joining the mailing list, please send email to hyesoon@cc.gatech.edu 

















% LocalWords:  Macsim MacSim NVIDIA PTX multicore RISC uops microarchitecture
% LocalWords:  NoC SMT McPat architecreus sandybridge begingroup renewcommand
% LocalWords:  descriptionlabel textit hspace labelsep cs firmlist endgroup
